ZCB Pricing

### 2018-07-24 ZCB Pricing .Rmd
Modified CN

CN <- function(alpha, beta, sigma, r,T, I, J){
  # I = partition of time interval
  # J = partition of short rate interval

  X <- length(I) # number of time grid points
  Y <- length(J) # number of rate grid points

  nr <- Y - 1 # number of rows

  dr <- J[2] - J[1]
  dt <- T/X

  #===========================================================================================
  # Define the following functions for j = 1,...,nr at each time point i

  pd <- function(j){
    (alpha -beta*J[j+1])/(2*dr) - sigma^2/(4*dr^2)
  }

  pm_1 <- function(j){
    J[j+1]/2 + 1/dt + sigma^2/(2*dr^2)
  }

  pm_2 <- function(j){
    -J[j+1]/2 + 1/dt - sigma^2/(2*dr^2)
  }

  pu <- function(j){
    - (alpha -beta*J[j+1])/(2*dr) - sigma^2/(4*dr^2)
  }

@@

  Diag_1 <- matrix(0,nrow = nr,ncol = nr)
  Diag_2 <- matrix(0,nrow = nr,ncol = nr)

  # Main diagonal of matrix 1
  for (j in 1:nr){
    Diag_1[j,j] <- pm_1(j)

@@

  # Filling lower diagonal of matrix 1
  for (j in 2:nr){
    Diag_1[j,j-1] <- pd(j)
  }

  # Filling upper diagonal of matirx 1
  for (j in 1:(nr-1)){
    Diag_1[j,j+1] <- pu(j)
  }

  # Main diagonal of matrix 2
  for (j in 1:nr){
    Diag_2[j,j] <- pm_2(j)

@@

  # Filling lower diagonal of matrix 2
  for (j in 2:nr){
    Diag_2[j,j-1] <- -pd(j)
  }

  # Filling upper diagonal of matirx 2
  for (j in 1:(nr-1)){
    Diag_2[j,j+1] <- -pu(j)
  }

  #===========================================================================================
  # Constructing more matricies and iterating the procedure from maturity to time 0
  # These matricies take care of the boundary conditions
  C_1 <- matrix(0,nrow = nr,ncol = 1)
  C_1[1,1] <- pd(1)
  C_1[nr,1] <- pu(nr)

  C_2 <- matrix(0,nrow = nr,ncol = 1)
  C_2[1,1] <- -pd(1)
  C_2[nr,1] <- -pu(nr)

  # Vector of bond price values at time i
  Bond_values <- matrix(1,nrow = nr, ncol = 1)

  for (i in I){
    Inv <- solve(Diag_1)
    RHS <- Diag_2%*%Bond_values + C_2 - C_1
    Bond_values <- Inv%*%RHS
  }

@@

G <- CN(0.08,0.8,0.005,0.05, T=5, I=1:365, J = seq(-0.3,0.5,0.01))

@@

xvec <- seq(-0.3,0.5,0.01)
S <- NULL
for (r in 1:length(xvec)){
  S[r] <- bond_price(0.08,0.8,0.005,0,1,xvec[r])
}
plot(G, x = xvec[1:length(xvec)-1],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank - Nicolson vs Known Solution")
lines(xvec,S, col ="blue", lty =1.5)
```

```{r}
# Crank Nicolson 2.0

CN_2 <- function(alpha = 0.08,beta =0.8,sigma=0.005,T=5,r =0.05,I = 1:1250, J = seq(-0.3,0.5,0.01)){

  M <- length(J)

>>>>

CN <- function(alpha = 0.08, beta = 0.8, sigma = 0.005, r = 0.08, T =5 , I = 1:1250==, J = seq(-0.3,0.5,0.01)){
  # I = partition of time interval
  # J = partition of short rate interval

  M <- length(J)
  N <- length(I)

  dt <- T/N
  dr <- J[2] -J[1]
  #===========================================================================================
  # Define the following functions for j = 1,...,M at each time point i

  pd <- function(j){
    (alpha -beta*J[j])/(4*dr) - sigma^2/(4*(dr^2))
  }

  pm <- function(j){
    sigma^2/(2*(dr^2)) + J[j]/2
  }

  pu <- function(j){
    -(alpha -beta*J[j])/(4*dr) - sigma^2/(4*(dr^2)) 
  }

@@

  Diag_1 <- matrix(0,nrow = M,ncol = M)
  Diag_2 <- matrix(0,nrow = M,ncol = M)

  # Main diagonal of matrix 1
  for (j in 1:M){
    Diag_1[j,j] <- -1/dt - pm(j)

@@

  # Filling lower diagonal of matrix 1
  for (j in 2:M){
    Diag_1[j,j-1] <- -pd(j)
  }

  # Filling upper diagonal of matirx 1
  for (j in 1:M-1){
    Diag_1[j,j+1] <- -pu(j)
  }

  # Main diagonal of matrix 2
  for (j in 1:M){
    Diag_2[j,j] <- -1/dt + pm(j)

@@

  # Filling lower diagonal of matrix 2
  for (j in 2:M){
    Diag_2[j,j-1] <- pd(j)
  }

  # Filling upper diagonal of matirx 2
  for (j in 1:M-1){
    Diag_2[j,j+1] <- pu(j)
  }

  #===========================================================================================
  # Constructing more matricies and iterating the procedure from maturity to time 0

  Bond_values <- matrix(1,nrow = M, ncol = 1)

  # C_1 <- matrix(0,nrow = M,ncol = 1)
  # C_1[1,1] <- -pd(1)
  # C_1[M,1] <- -pu(M)
  # 
  # C_2 <- matrix(0,nrow = M,ncol = 1)
  # C_2[1,1] <- pd(1)
  # C_2[M,1] <- pu(M)

  for (i in 1:(length(I)+1)){
    Inv <- solve(Diag_1)
    RHS <- Diag_2%*%Bond_values 
    Bond_values <- Inv%*%RHS
  }

@@

@@

xvec <- seq(-0.3,0.5,0.01)
S <- NULL
for (r in 1:length(xvec)){
  S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
}
plot(CN(), x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank - Nicolson vs Known Solution")
lines(xvec,S, col ="blue", lty =1.5)
```
